---
title: "rMAFdb"
author: 
    name: "Nicolò Rossi"
    affiliation: "University of Udine"
    email: "olocin.issor@gmail.com"
date: "09/02/2021"
geometry: margin=2cm
output:
    html_document:
        toc_float: true
        df_print: paged
vignette: >
    %\VignetteEncoding{UTF-8}
    %\VignetteIndexEntry{rMAFdb: Create databases to manage MAF files}
    %\VignetteEngine{knitr::rmarkdown}
---

```{r style, echo = FALSE, results = 'asis'}
BiocStyle::markdown()
```

```{r,setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=F, warning=F)
# --- libs
library(tidyverse)
library(dbplyr)
library(DBI)
library(tictoc)
library(rprojroot)
library(rMAFdb)
```

This files shows how to use the current implementation of the MAFdb. The goal
of this implementation is to allow fast queries on MAF data without 
loosing compatibility with MAF analyzing software as the output of each query
can be easily converted to a regular MAF file.

## Connect to database:

```{r}
user <- "postgres"
con <- dbConnect(RPostgreSQL::PostgreSQL(), 
  host = "127.0.0.1",
  user = user,
  dbname = "anotherMAFtest",
  password = "1234"
)
```

## load database

```{r}
tic()
filename <- find_root_file("inst", "extdata", "small.maf", criterion = has_file("DESCRIPTION"))
db <- MAFdb.load(con, filename, reset = T)
toc()
print(db)
```

## re-open db

```{r}
db2 <- MAFdb(con)
dbListTables(db2@con)
```

## Run in case of persisting connections:

```{r, eval=FALSE}
# close all connection to PostreSQL
lapply(dbListConnections(RPostgreSQL::PostgreSQL()), dbDisconnect)
```

## Test operations

```{r}
example.text <- c(
  paste("1","N;M","C","D","A;1","A=2","nome:cognome","Marco,Caco", sep="\t"),
  paste("1","N;M","C","D","A;1","A=2","nome:cognome","Marco,Caco", sep="\t"),
  paste("1","N;M","C","D","A;1","A=2","nome:cognome","Marco,Caco", sep="\t"),
  paste("1","N;M;S;T","C","D","A;1","A=2","nome:cognome","Marco,Caco", sep="\t")
)
# inner function to create db insertion query
cat(test_MAFdb("example", example.text, c("c1","list","c3","c4", "list_cols", "kv_test", "keys", "values"), c(2,3,1,1,3,3,3,3), 0))
```

## Test operations on MAF

```{r}
db["maf"] %>% group_by(hugo_symbol) %>% summarise(n=n()) %>% arrange(desc(n)) %>% as.data.frame()
```


```{r}
# # A full example
# user <- "postgres"
# con <- dbConnect(RPostgreSQL::PostgreSQL(), 
#   host = "127.0.0.1",
#   user = user,
#   dbname = "anotherMAFtest",
#   password = "1234" #rstudioapi::askForPassword(paste("Enter", user, "password:"))
# )
# tic()
# db <- MAFdb.load(con, "~/Documenti/TCGA-BRCA-VCF-Datasets/gdc_download_20210128_084228.661394/053f01ed-3154-4aea-9e7f-932c435034b3/only_some.maf", reset = T, limit=10000)
# toc()
# print(db)
# 
# db["maf"] %>% group_by(hugo_symbol) %>% summarise(n=n()) %>% arrange(desc(n)) %>% as.data.frame()
# 
# dbDisconnect(con)
```



